---
title: "Interpretation of Results"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Interpretation of Results}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Target Market Share

[brief description of Target Market Share metric]

For detailed information about the Target Market Share metric and how it is calculated, see the [Metrics appendix](cookbook_metrics.html#market-share-approach).

### `target_market_share()` function

The `target_market_share()` function calculates the Target Market Share metric and outputs a table including the calculated targets at the portfolio level or at the company level, depending on the options selected.

#### Explanation of Output

The primary columns/variables of interest in the output are the `production` and `metric` variables. What the `production` variable represents depends on the values in all of the columns that precede it, and in particular the `metric` column. If the value in the `metric` column on the same row is `"projected"`, then the value in the `production` variable will represent the production level of your portfolio based on the ABCD data for that sector/technology/year/scenario/etc. If the value in the `metric` column on the same row begins with `"target_"`, e.g. `"target_cps"`, then the value in the `production` variable will represent the target level of production for that sector/technology/year/scenario/etc. based on the ABCD start year production value of your portfolio modified to be relative to the scenario data for the given year. If the value in the `metric` column on the same row is `"corporate_economy"`, then the value in the `production` variable will represent [the total production levels of the entire sector adjusted by the start year production level of your portfolio, which can be used aa a benchmark to compare to your portfolio's production levels].

The `technology_share` and `percentage_of_initial_production_by_scope` variables also contain values of interest, but they are derivatives of the values contained in the `production` variable. The `technology_share` variable tells the share of the row's technology within its sector, relative to the production values of other technologies in the same sector, similar to what is shown in the [technology mix plots](cookbook_interpretation.html#technoloy-mix-plot), relative to whatever is defined in the `metric` column in that row. The `percentage_of_initial_production_by_scope` variable shows the percent change of the production value from the prior year.

If you use the `by_company = TRUE` option of the `target_market_share()` function, most of what's said above is true except relative to the company listed in that row in the `name_abcd` column.

For detailed information about the table output of the `target_market_share()` function and its columns, see the [data dictionary](data_outputs.html#target_market_share-output).

#### Interpretation & Intuition

[2 or 3 sentences about interpretation]

[2 or 3 sentences about intuition]

### Technoloy Mix Plot

The technology mix metric focuses on technology shifts within the power, fossil fuels and automotive sectors, namely: (i) the changes in the technological processes by which outputs are produced (e.g. shift from coal-fueled to renewable-fueled power capacity), and (ii) changes in the nature of the output itself (e.g. shift from internal combustion engines to electric vehicles). This metric measures the bank’s relative exposure to the economic activities that are impacted by the transition to a low-carbon economy.

#### Explanation of Output

[2 or 3 sentence explanation on plot output]

#### Interpretation & Intuition

[2 or 3 sentences about interpretation]

[2 or 3 sentences about intuition]

```{r, message=FALSE, warning=FALSE, echo=FALSE}
library(pacta.loanbook)

market_share_targets_portfolio <-
  target_market_share(
    data = prioritize(match_name(loanbook_demo, abcd_demo)),
    abcd = abcd_demo,
    scenario = scenario_demo_2020,
    region_isos = region_isos_demo
  )

qplot_techmix(
  dplyr::filter(
    market_share_targets_portfolio,
    scenario_source == "demo_2020",
    sector == "power",
    region == "global",
    metric %in% c("projected", "corporate_economy", "target_sds")
  )
)

```

### Trajectory Plot

The production volume trajectory metric aims to measure the alignment of a portfolio’s projected production volumes, based on the five-year capital plans of companies, to those given in climate scenarios. It is used for the fossil fuels, power, and automotive sectors. Changes in production volumes result either from transfer of production from one technology to another (e.g. internal combustion engines to electric vehicles) or from sheer expansion or contraction in the production coming from the technology/fuel (e.g. a company brings a new coal-fired power plant online). Projected production volumes at a 5-year horizon are considered at the individual client level at the technology level. The resulting volume trajectories are then compared with the trends set as targets in climate scenarios.

#### Explanation of Output

[2 or 3 sentence explanation on plot output]

#### Interpretation & Intuition

[2 or 3 sentences about interpretation]

[2 or 3 sentences about intuition]

```{r, message=FALSE, warning=FALSE, echo=FALSE}
library(pacta.loanbook)

market_share_targets_portfolio <-
  target_market_share(
    data = prioritize(match_name(loanbook_demo, abcd_demo)),
    abcd = abcd_demo,
    scenario = scenario_demo_2020,
    region_isos = region_isos_demo
  )

qplot_trajectory(
  dplyr::filter(
    market_share_targets_portfolio,
    sector == "power",
    technology == "renewablescap",
    region == "global",
    scenario_source == "demo_2020"
  )
)
```

## Sectoral Decarbonization (SDA) Target

[brief description of SDA metric]

For detailed information about the Sectoral Decarbonization (SDA) metric and how it is calculated, see the [Metrics appendix](cookbook_metrics.html#sectoral-decarbonization-approach).

### `target_sda()` function

The `target_sda()` function calculates the Sectoral Decarbonization Target metric and outputs a table including the calculated targets at the portfolio level or at the company level, depending on the options selected.

#### Explanation of Output

The primary column/variable of interest in the output is the `emission_factor_value` variable. What the `emission_factor_value` variable represents depends on the values in all of the other columns, and in particular the `emission_factor_metric` column. If the value in the `emission_factor_metric` column on the same row is `"projected"`, then the value in the `emission_factor_value` variable will represent the physical emission intensity level of your portfolio based on the ABCD data for that sector/year/region/scenario/etc. If the value in the `emission_factor_metric` column on the same row begins with `"target_"`, e.g. `"target_cps"`, then the value in the `emission_factor_value` variable will represent the target level of physical emission intensity for that sector/year/region/scenario/etc. based on the ABCD start year production value of your portfolio modified to be relative to the scenario data for the given year. If the value in the `emission_factor_metric` column on the same row is `"corporate_economy"`, then the value in the `emission_factor_value` variable will represent [the total physical emission intensity levels of the entire sector adjusted by the start year physical emission intensity level of your portfolio, which can be used aa a benchmark to compare to your portfolio's production levels]. If the value in the `emission_factor_metric` column on the same row starts with `"adjusted_"`, then the value in the `emission_factor_value` variable will represent [?].

If you use the `by_company = TRUE` option of the `target_sda()` function, most of what's said above is true except relative to the company listed in that row in the `name_abcd` column.

For detailed information about the table output of the `target_sda()` function and its columns, see the [data dictionary](data_outputs.html#target_sda-output).

#### Interpretation & Intuition

[2 or 3 sentences about interpretation]

[2 or 3 sentences about intuition]

### Emission Intensity Plot

The emission intensity metric measures the average CO^2^ intensity of the portfolio in the steel and cement sector. This emission intensity is given as CO^2^/economic unit of output (for example, CO^2^/per ton of steel produced). This is then compared to an emission intensity reference point set by a climate scenario.

While this is not the main metric of choice for the largest sectors tackled in this methodology, the emission intensity of the activities financed by the portfolio is nonetheless the first metric in sectors for which no clear technology pathways have been set out (namely, steel and cement). Put differently, for these sectors, no zero-carbon alternative yet exists. As such, it is not possible to use the technology mix metric or the volume production volume trajectory metric to measure alignment. However, it is still imperative to steer capital in a way that aims to decrease carbon emissions in these sectors – hence the emission intensity metric is used.

#### Explanation of Output

[2 or 3 sentence explanation on plot output]

#### Interpretation & Intuition

[2 or 3 sentences about interpretation]

[2 or 3 sentences about intuition]

```{r, message=FALSE, warning=FALSE, echo=FALSE}
library(pacta.loanbook)

sda_targets <-
  target_sda(
    data = prioritize(match_name(loanbook_demo, abcd_demo)),
    abcd = abcd_demo,
    co2_intensity_scenario = co2_intensity_scenario_demo,
    region_isos = region_isos_demo
  )

qplot_emission_intensity(
  dplyr::filter(
    sda_targets,
    sector == "cement",
    region == "global"
  )
)
```

---

**PREVIOUS CHAPTER:** [Running the Analysis](cookbook_running_the_analysis.html)

**NEXT CHAPTER:** [Advanced Use Cases](cookbook_advanced_use_cases.html)
