---
title: "Advanced Use Cases"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Advanced Use Cases}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Suppose I have a loanbook containing a loan to "Acme Co."

```{r, message = FALSE, R.options = list(width = 400)}
library(pacta.loanbook)

loanbook <- 
  data.frame(
    id_loan = "L1",
    id_direct_loantaker = "C123",
    name_direct_loantaker = "Acme Co.",
    id_ultimate_parent = "C45",
    name_ultimate_parent = "Acme Holdings",
    loan_size_outstanding = 1e7,
    loan_size_outstanding_currency = "USD",
    loan_size_credit_limit = 1e8,
    loan_size_credit_limit_currency = "USD",
    sector_classification_system = "NACE",
    sector_classification_direct_loantaker = "D35.12"
  )

loanbook
```

When I try to match it, there are no results because the ABCD data does not have any data associated with a "Acme Co."

```{r, message = FALSE, R.options = list(width = 400)}
match_name(loanbook = loanbook, abcd = abcd_demo)
```

If I had data for Acme Co. from a different source, I could supplement my ABCD data with this information, and with the combined ABCD, I get a matched loan.

```{r, message = FALSE, R.options = list(width = 400)}
abcd_addition <-
  data.frame(
    company_id = rep("175", 5),
    name_company = rep("Acme Co.", 5),
    lei = rep("18500033XH6RG332SX57", 5),
    sector = rep("power", 5),
    technology = rep("hydrocap", 5),
    production_unit = rep("MW", 5),
    year = 2020L:2024L,
    production = c(12000, 12000, 12375, 13000, 13000),
    emission_factor = rep(NA, 5),
    plant_location = rep("MY", 5),
    is_ultimate_owner = rep(TRUE, 5),
    emission_factor_unit = rep("tonnes of CO2 per per hour per MW", 5)
  )

abcd_addition

abcd_combined <- rbind(abcd_demo, abcd_addition)

match_name(loanbook = loanbook, abcd = abcd_combined)
```

---

**PREVIOUS CHAPTER:** [Interpretation of Results](cookbook_interpretation.html)

**NEXT CHAPTER:** [Metrics](cookbook_metrics.html)
