---
title: "Running the Analysis"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Running the Analysis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Running the Analysis

This section outlines the key steps for running the PACTA for Banks analysis, beginning with a high-level overview followed by a detailed breakdown of each step. Code snippets are provided to ensure a straightforward implementation in your own R environment.

## Structure of the Workflow

If you have prepared or obtained all required input datasets as outlined in [Preparatory Steps](cookbook_preparatory_steps.html), you can then proceed with the PACTA for Banks analysis through the following main steps:

1.  **Setup**: Load the necessary packages and import the data.
2.  **Matching process**: Match counterparties in the loan book to companies in the asset-based company data.
3.  **Calculate PACTA metrics**: Run the analysis to assess loan book alignment with transition scenario benchmarks.
4.  **Plot PACTA metrics**: Generate standard PACTA visualizations to support result interpretation.

```{r workflow_structure, echo=FALSE, fig.cap='Fig. 1: Structure of the Workflow', fig.align='center'}
DiagrammeR::mermaid('
  graph TB;
    id1("Setup") --> id2("Matching process");
    id2("Matching process") --> id3("Calculate PACTA metrics");
    id3("Calculate PACTA metrics") --> id4("Visualize PACTA metrics");
    classDef nodeStyle fill: #45cfcc, stroke: #000, stroke-width: 2px;
    class id1,id2,id3,id4 nodeStyle;
    click id1 "#setup";
    click id2 "#matching-process";
    click id3 "#calculate-pacta-alignment-metrics";
    click id4 "#visualize-pacta-alignment-metrics";
')
```

These steps are generally sequential, but achieving the best possible match rate often requires multiple iterations. The matching process may need to be refined and repeated to improve accuracy. The following sections provide a detailed breakdown of each step.

## Setup

We use the `{pacta.loanbook}` package for key functions and example datasets. Additionally, we leverage `{dplyr}`, `{readxl}`, and `{readr}` for optional but convenient data manipulation and import functions.

```{r, message=FALSE}
library(pacta.loanbook)
library(dplyr)
library(readxl)
library(readr)
```

## Import Data

We need two datasets to begin: a [loanbook](cookbook_preparatory_steps.html#raw-loan-book) and an [asset-based company dataset (abcd)](cookbook_preparatory_steps.html#asset-based-company-data-abcd). For more detail about the necessary structure of these datasets, see the data dictionaries for [loanbook](data_loanbook.html) and [abcd](data_abcd.html).

To simulate having these data files prepared, we will use the demo data included in the `{pacta.loanbook}` package to create example XLS files using the `{writexl}` package.

```{r}
library(writexl)

writexl::write_xlsx(
  x = loanbook_demo,
  path = file.path(tempdir(), "loanbook.xlsx")
)

writexl::write_xlsx(
  x = abcd_demo,
  path = file.path(tempdir(), "abcd.xlsx")
)
```

Typically, these data files are stored in XLS files on your computer. As an example, they could be imported as in the code below using the `{readxl}` package, however, if you use custom data that does not strictly follow the format as defined in [the previous section](cookbook_preparatory_steps.html), you may need to adjust the import code and/or do some data manipulation in R after importing.

```{r, R.options = list(width = 400)}
loanbook <- readxl::read_excel(path = file.path(tempdir(), "loanbook.xlsx"))

loanbook

abcd <- readxl::read_excel(path = file.path(tempdir(), "abcd.xlsx"))

abcd
```

## Matching Process

The next step after loading all required input files is to run the matching process, where you will match loans from the loanbook data with production data from the ABCD dataset

The matching process is divided into three main steps:

- Apply Matching Algorithm – Calculate match precision scores between the loan book and ABCD datasets.
- Validate Matches – Manually review matches, selecting the correct company when multiple exceed the threshold score.
- Prioritize Matches – Rank validated matches by priority level.

The following sections provide a detailed breakdown of each step.

### Score the match precision between the loanbook and abcd datasets

`match_name()` scores the match between names in a loanbook dataset and names in an asset-based company dataset. The names come from the columns `name_direct_loantaker` and `name_ultimate_parent` of the loanbook dataset, and from the column `name_company` of the asset-based company dataset. In the loan book data set, it is possible to optionally add any number of `name_intermediate_parent_*` columns, where `*` indicates the level up the corporate tree from `direct_loantaker`.

The raw names are internally transformed applying best-practices commonly used in name matching algorithms, such as:

- Remove special characters
- Replace language specific characters
- Abbreviate certain names to reduce their importance in the matching
- Remove corporate suffixes when necessary
- Spell out numbers to increase their importance

The similarity is then scored between the internally-transformed names of the loanbook against the names in the abcd. For more information on the scoring algorithm used, see `stringdist::stringsim()`.

The basic usage of `match_name()` is as follows:

```{r, R.options = list(width = 400)}
matched <- match_name(loanbook, abcd)

matched
```

`match_name()` defaults to scoring matches between name strings that belong to the same sector. This implies that a potential match will only be shown if the names in the loanbook and the ABCD are sufficiently similar AND the loan is classified in the same sector as the company activity in the ABCD Using `by_sector = FALSE` removes this limitation -- increasing computation time, and the number of potentially incorrect matches to manually validate. In most cases, it is recommended to keep `by_sector = TRUE`. However, lifting the restriction can be helpful in cases where the sector classification in the loanbook is not reliable or no sector classification is available at all. Below you can see that the removal of the restriction increases the number of potential matches.

The `match_name()` function, by default, scores matches between name strings within the same sector. This means a potential match is shown only if:
- The names in the loan book and ABCD dataset are sufficiently similar.
- The loan is classified in the same sector as the company activity in the ABCD dataset.

Setting `by_sector = FALSE` removes this restriction, which:
- Increases computation time.
- Increases the number of potential (but possibly incorrect) matches requiring manual validation.

In most cases, keeping `by_sector = TRUE` is recommended. However, disabling the sector restriction can be useful when sector classifications in the loan book are unreliable or missing. Below, you can see how removing the restriction increases the number of potential matches.

```{r}
match_name(loanbook, abcd, by_sector = FALSE) %>% nrow()

# Compare to
match_name(loanbook, abcd, by_sector = TRUE) %>% nrow()
```

The `min_score` argument sets a minimum threshold score for matching precision. This helps by:
- Filtering out imprecise matches by setting a higher threshold.
- Adding more potential matches if the default suggestions don’t provide enough coverage.

The default value is 0.8, but you can adjust it between 0 and 1. A higher score means stricter matching, resulting in fewer potential matches.

The example below sets the threshold to 0.9:

```{r}
match_name(loanbook, abcd, min_score = 0.9) %>%
  pull(score) %>%
  range()
```

### Manually validate matches

After calculating initial match scores, you must manually review the suggested matches to decide which to keep or remove. This step is critical for ensuring a high quality match result, especially in text-based matching, where similar company names may not actually refer to the same entity.

Manual validation helps to:
- Prevent incorrect matches from affecting the analysis.
- Ensure accuracy in linking loan book data to the ABCD dataset.
- Improve overall match precision, especially when iterating to enhance coverage.

Since this step isn’t automated, it requires effort, often making it the most time-consuming part of the process.

To begin, save the output of match_name() to a CSV file for review. For example, using {readr}:

```{r}
readr::write_csv(x = matched, file = file.path(tempdir(), "matched.csv"))
```

After exporting the match results, you must manually review, edit, and save the data:
- **Open the file** – Load `matched.csv` in a spreadsheet editor (Excel, Google Sheets, etc.).
- **Compare matches** – Verify if the `name` (loan book) and `name_abcd` (ABCD) correspond to the same entity. Use additional details (sector, company structure, internal data) to improve accuracy.
- **Edit the data**:
  - If the match is valid, set the `score` value to `1`.
  - If the match is incorrect or uncertain, leave the `score` as-is or set it to a value other than `1`.
- **Save the edited file**: as `valid_matches.csv`.

Once validated, re-import the edited file into R, for example, using `{readr}`:

```{r echo=FALSE, results='hide', message=FALSE}
# simulating that the user did the above process and saved a new valid_matches.csv
file.copy(from = file.path(tempdir(), "matched.csv"), to = file.path(tempdir(), "valid_matches.csv"))
```

```{r}
valid_matches <- readr::read_csv(file = file.path(tempdir(), "valid_matches.csv"), show_col_types = FALSE)
```

You can find more detailed information about the matching process under the header "PACTA for Banks Training Webinar 2" in the [training materials section of the PACTA for Banks website](https://pacta.rmi.org/pacta-for-banks-2020/training-materials/) and in the [corresponding slide deck](https://pacta.rmi.org/wp-content/uploads/2020/12/PACTA-for-Banks-Training-Webinar-2-Matching-a-loan-book-to-physical-assets-in-the-real-economy-.pdf).

### Prioritize validated matches by level

The validated dataset may have multiple matches per loan. Consider the case where a loan is given to "Acme Power USA", a subsidiary of "Acme Power Co.". There may be both "Acme Power USA" and "Acme Power Co." in the `abcd`, and so there could be two valid matches for this loan. To get the best match only, use `prioritize()` -- it picks rows where `score` is 1 and `level` per loan is of highest `priority`:

```{r}
some_interesting_columns <- c("id_2dii", "level", "score")

prioritized_matches <-
  valid_matches %>%
  prioritize()

prioritized_matches %>% select(all_of(some_interesting_columns))
```

By default, highest priority refers to the most granular match (`direct_loantaker`). The default priority is set internally via `prioritize_level()`.

```{r}
prioritize_level(valid_matches)
```

You may use a different priority. One way to do that is to pass a function to `priority`. For example, use `rev()` to reverse the default priority.

```{r}
valid_matches %>%
  prioritize(priority = rev) %>%
  select(all_of(some_interesting_columns))
```

### A Note on Sector Classifications and the `borderline` Flag

#### A note on sector classification

Matches are preferred when the sector from the `loanbook` matches the sector from the `abcd`. The `loanbook` sector is determined internally by mapping the sector classification code from the loan book to a PACTA sector, using the `sector_classification_system` and `sector_classification_direct_loantaker` columns. Currently, the following options are supported for `sector_classification_system`, specified in `sector_classifications`:

> `r unique(sector_classifications$code_system)`

#### The `borderline` flag

An issue arises when, for example, a company is classified in the "power transmission" sector. In a perfect world, these companies would produce no electricity, and we would not try to match them. In practice, however, we find there is often overlap, as companies may have integrated business models that span multiple steps of the supply chain or sector classification systems do not break down every code clearly enough to map it to PACTA sectors unambiguously. For this reason, we introduced the `borderline` flag.

In the example below, we see two classification codes coming from the NACE classification standard:

```{r}
nace_classification %>% 
  filter(code %in% c("D35.11", "D35.14", "D35.1"))
```

Notice that the code D35.11 corresponds to power generation. This is an identical match to `power` sector in PACTA, and thus the `borderline` flag is set to `FALSE`. In contrast, code D35.14 corresponds to the distribution of electricity. In a perfect world, we would set this code to `not in scope`, however there is still a chance that these companies produce electricity. For this reason, we have mapped it to `power` with `borderline = TRUE`. Finally, code D35.1 corresponds to the wider electricity sector, covering "Electric power generation, transmission and distribution". This is a case where the granularity is insufficient to unambiguously match the code to the `power` sector as defined in PACTA, and thus the `borderline` flag is set to `TRUE`.

In practice, if a company has a sector code with `borderline` is `TRUE` and *is* matched, then consider the company in scope. If it has a `borderline` value `TRUE` and *is not* matched, then consider it out of scope.

### Optional: Prepare own sector classification mapper

If you can obtain sector codes in any one of those classification systems for your loan book, it is strongly recommended using them. If you do not have your loans mapped to any of these systems, you can either run the matching without a sector classification (see above), or you can use a custom sector classification system.

If you want to use your own custom sector classification system, you will need to create a file that follows the same structure as the sector classification files in `sector_classifications`, that is, the file needs to contain the following columns (of the following types):

```{r cols_custom_sector_classification, echo = FALSE, results = 'asis'}
pacta.loanbook:::list_col_names_and_types(sector_classifications)
```

Please notice that when manually preparing a custom sector classification file, you need to decide for every code of your mapping system which PACTA sector the code maps to. This requires the system to be relatively granular to capture the nuances of the supply chains of the companies in your loan book. As discussed above, any sector code that is not unambiguously in scope or out of scope for a given PACTA sector should be marked `TRUE` in the `borderline` column. Any sector code that is clearly not in scope should be marked `FALSE` and receive the sector value `not in scope`. Any sector code that is clearly in scope should be marked `FALSE` for `borderline` and receive the PACTA sector value that it maps to in the `sector` column.

**ADD EXAMPLE**

### Calculate the Match Success Rate

```{r include=FALSE}
sector_in_scope <- glue::glue_collapse(
  unique(abcd$sector), sep = ", ", last = ", and "
)
```

`{pacta.loanbook}` allows you to match loans from your loanbook to the companies in an asset-based company dataset. However, not all loans will have a match -- some companies may be missing from the ABCD dataset, or they may operate outisde the PACTA focus sectors (`r sector_in_scope`).

To assess how much of your loan book is successfully matched, you can circulate matching coverage in two ways:

(1) By dollar value: Measure the portion of your loan book covered, using one of the `loan_size_*` columns. 

(2) By company count: Count the number of companies matched. 

To visualize matching coverage, first load the `{ggplot2}` package:

```{r}
library(ggplot2)
```

We will use the example datasets created in the previous section. To illustrate the point, we create a `loanbook` dataset with two mismatched loans:

```{r}
loanbook <- loanbook %>% 
  mutate(
    name_ultimate_parent = 
      ifelse(id_loan == "L1", "unmatched company name", name_ultimate_parent),
    sector_classification_direct_loantaker = 
      ifelse(id_loan == "L2", "99", sector_classification_direct_loantaker)
  )
```

We will then run the matching algorithm on this loanbook:

```{r}
matched <- loanbook %>% 
    match_name(abcd) %>% 
    prioritize()
```

The `matched` dataset contains _only_ successfully matched loans. To determine coverage, we need to refer back to the original loanbook dataset and classify each loan according to the PACTA sectors using the `sector_classification_direct_loantaker` column.

To achieve this, we merge loanbook with the `sector_classifications` dataset, which includes all sector classification standards used by PACTA. However, there are two technical caveats to consider:

(1) Column name differences: The datasets use different column names for sector classifications. We use `dplyr::left_join()` with the `by` argument to merge:

- `sector_classification_system` and `sector_classification_direct_loantaker` (from `loanbook`)
- `code_system` and `code` (from `sector_classifications`)

(2) Data type mismatch: The sector classification codes have different data types in the two datasets. To prevent errors in `dplyr::left_join()`:
- We convert `sector_classification_direct_loantaker` to match the type of `code` before merging.
- After merging, we restore its original type.

```{r}
merge_by <- c(
    sector_classification_system = "code_system",
    sector_classification_direct_loantaker = "code"
  )

loanbook_with_sectors <- loanbook %>% 
  left_join(sector_classifications, by = merge_by) %>% 
  mutate(sector_classification_direct_loantaker = as.character(sector_classification_direct_loantaker))
```

To generate the `coverage` dataset, we merge these two datasets together:

``` {r}
coverage <- left_join(loanbook_with_sectors, matched) %>% 
  mutate(
    loan_size_outstanding = as.numeric(loan_size_outstanding),
    loan_size_credit_limit = as.numeric(loan_size_credit_limit),
    matched = case_when(
      score == 1   ~ "Matched", 
      is.na(score) ~ "Not Matched",
      TRUE         ~ "Not Matched"
    ),
    sector = case_when(
      borderline == TRUE & matched == "Not Matched" ~ "not in scope",
      TRUE ~ sector
    )
  )
```

#### 1. Calculate loanbook coverage by dollar value

Using the `coverage` dataset, we can measure total loan book coverage based on dollar value. To facilitate this, we define two helper functions:

(1) A function to calculate coverage by dollar value.
(2) A plotting function to visualize coverage.

```{r}
dollar_value <- function(data, ...) {
  data %>% 
    summarize(loan_size_outstanding = sum(loan_size_outstanding), .by = c(matched, ...))
}

plot_coverage <- function(data, x, y) {
  ggplot(data) + 
    geom_col(aes({{x}}, {{y}}, fill = matched)) +
    # Use more horizontal space -- avoids overlap on x axis text
    theme(legend.position = "top")
}
```

Let's first explore all loans.

```{r}
coverage %>% 
  dollar_value() %>% 
  plot_coverage(matched, loan_size_outstanding)
```

To calculate the total, in-scope, loanbook coverage: 

```{r}
coverage %>% 
  filter(sector != "not in scope") %>% 
  dollar_value() %>% 
  plot_coverage(matched, loan_size_outstanding)
```

You may break-down the plot by sector: 

```{r}
coverage %>% 
  dollar_value(sector) %>% 
  plot_coverage(sector, loan_size_outstanding)
```

Or even further, by matching level:

```{r}
coverage %>% 
  mutate(matched = case_when(
    matched == "Matched" & level == "direct_loantaker"      ~ "Matched DL",
    matched == "Matched" & level == "intermediate_parent_1" ~ "Matched IP1",
    matched == "Matched" & level == "ultimate_parent"       ~ "Matched UP",
    matched == "Not Matched"                                ~ "Not Matched",
    TRUE                                                    ~ "Catch unknown"
  )) %>% 
  dollar_value(sector) %>% 
  plot_coverage(sector, loan_size_outstanding)
```

#### 2. Count the number of companies matched

Another useful metric is the number of companies in your loan book that were successfully matched. The most relevant level for this analysis is likely the `direct_loantaker` level.

``` {r}
companies_matched <- coverage %>% 
  summarize(no_companies = n_distinct(name_direct_loantaker), .by = c(sector, matched))

companies_matched %>% 
  plot_coverage(sector, no_companies)
```

### Optional: Handling misclassified loans

A misclassified loan occurs when a counterparty is incorrectly identified as belonging to a PACTA sector based on the sector classification in the loan book.

Why does misclassification matter?
- It artificially lowers match success rates by expecting matches that don’t exist in the ABCD dataset.
- Iterating the matching process won’t help—if a company doesn’t operate in an in-scope sector, no adjustments will create a valid match.
- A reliable match success rate requires an accurate denominator, meaning only loans truly within an in-scope sector should be included.

Misclassification is typically identified manually by reviewing unmatched counterparties to determine if they should be in scope. Since this process can be time-consuming, it’s best to prioritize unmatched loans with the largest amounts, as they have the greatest impact on the match success rate.

Since misclassified loans cannot be matched, leaving them in the dataset skews results. While correction isn’t mandatory, adjusting large misclassified loans is strongly recommended for more accurate analysis.

#### Options for Handling Misclassified Loans

Once misclassified loans have been identified, there are two options:

(1) Correct the classification in the loanbook:
- Update the raw loanbook to reflect the correct sector.
- Re-run the matching process to ensure the loan is matched appropriately
- Keep documentation of changes for replicability

(2) Adjust match success rate calculation:
- If modifying the raw loanbook isn't possible, exclude misclassified loans from the success rate calculation.
- Create a `loans_to_remove.csv` file containing a single column, `id_loan`, listing the misclassified loans. 
- Remove these loans from the match success calculation to avoid misleading results. 

The first option is generally preferred, as it ensures loans are assigned to the correct sector.

Once the list of misclassified loans is identified, there are two broad options to appropriately these cases. 

#### Example

Suppose a loan with ID L255 is falsely classified as a steel company but actually produces steel-based products, making it part of the downstream value chain rather than primary steel production. Since it cannot be matched to ABCD, but the sector classification cannot be changed, we handle it by creating a CSV file with its ID.

This correction process can be done programmatically or manually, ensuring more accurate match success rate reporting.

```{r}
readr::write_csv(
  x = tibble(id_loan = "L255"),
  file = file.path(tempdir(), "loans_to_remove.csv")
)

```

The `loans_to_remove.csv` file should have just one column, `id_loan`, and therefore be structured as follows:

```{r, echo = FALSE, results = 'asis'}
pacta.loanbook:::list_col_names_and_types(tibble::tibble(id_loan = "x"))
```

We then read in the file and remove the misclassified loan from the match success rate calculation. We compare the coverage before and after the removal of the misclassified loan to see the impact of the correction. For demonstration purposes, we artificially increase the loan_size_outstanding of the affected counterparty while focusing on the steel sector only, to see the clear impact.

```{r, message=FALSE}
coverage_compare <- coverage %>% 
  mutate(
    loan_size_outstanding = ifelse(id_loan == "L255", 50000000, loan_size_outstanding)
  ) %>% 
  filter(sector == "steel")

coverage_compare %>%
  mutate(matched = case_when(
    matched == "Matched" & level == "direct_loantaker"      ~ "Matched DL",
    matched == "Matched" & level == "intermediate_parent_1" ~ "Matched IP1",
    matched == "Matched" & level == "ultimate_parent"       ~ "Matched UP",
    matched == "Not Matched"                                ~ "Not Matched",
    TRUE                                                    ~ "Catch unknown"
  )) %>% 
  dollar_value(sector) %>% 
  plot_coverage(sector, loan_size_outstanding)

loans_to_remove <- readr::read_csv(file.path(tempdir(), "loans_to_remove.csv"))

coverage_corrected <- coverage_compare %>% 
  anti_join(loans_to_remove, by = "id_loan")

coverage_corrected %>% 
  mutate(matched = case_when(
    matched == "Matched" & level == "direct_loantaker"      ~ "Matched DL",
    matched == "Matched" & level == "intermediate_parent_1" ~ "Matched IP1",
    matched == "Matched" & level == "ultimate_parent"       ~ "Matched UP",
    matched == "Not Matched"                                ~ "Not Matched",
    TRUE                                                    ~ "Catch unknown"
  )) %>% 
  dollar_value(sector) %>% 
  plot_coverage(sector, loan_size_outstanding)
```

## Calculate PACTA alignment metrics

PACTA alignment metrics can be calculated using two approaches: the Market Share Approach and the Sectoral Decarbonization Approach.

### Market Share Approach

The [Market Share Approach](cookbook_metrics.html#market-share-approach) sets scenario targets based on the production of a technology within a sector. For example, it can define targets for electric vehicle production in the automotive sector. This approach is recommended for sectors with detailed technology roadmaps.

Targets can be set at the portfolio level:

```{r, R.options = list(width = 400)}
# Use these datasets to practice but eventually you should use your own data.
scenario <- scenario_demo_2020
regions <- region_isos_demo

market_share_targets_portfolio <-
  target_market_share(
    data = prioritized_matches,
    abcd = abcd,
    scenario = scenario,
    region_isos = regions
  )

market_share_targets_portfolio
```

or at the company level:

```{r market-share-targets-company, R.options = list(width = 400)}
market_share_targets_company <-
  target_market_share(
    data = prioritized_matches,
    abcd = abcd,
    scenario = scenario,
    region_isos = regions,
    by_company = TRUE, # Output results at company-level
    weight_production = FALSE
  )

market_share_targets_company
```

These results can be saved/written to a CSV file for potential input to other models and software, for example:

```{r}
readr::write_csv(x = market_share_targets_portfolio, file = file.path(tempdir(), "market_share_targets_portfolio.csv"))
readr::write_csv(x = market_share_targets_company, file = file.path(tempdir(), "market_share_targets_company.csv"))
```

Remember to replace `tempdir()` with the path to the directory that you wish to save your files in.

### Sectoral Decarbonization Approach

The [Sectoral Decarbonization Approach](cookbook_metrics.html#sectoral-decarbonization-approach) sets scenario targets based on a sector's emission factor. For example, it can define targets for the average emission factor in the cement sector. This approach is recommended for sectors without detailed technology roadmaps.


```{r sda-targets, R.options = list(width = 400)}
# Use this dataset to practice but eventually you should use your own data.
co2 <- co2_intensity_scenario_demo

sda_targets <-
  target_sda(
    data = prioritized_matches,
    abcd = abcd,
    co2_intensity_scenario = co2,
    region_isos = regions
  ) %>% 
  filter(sector == "cement", year >= 2020)

sda_targets
```

or at the company level:

```{r sda-targets-company, R.options = list(width = 400)}
sda_targets_company <-
  target_sda(
    data = prioritized_matches,
    abcd = abcd,
    co2_intensity_scenario = co2,
    region_isos = regions,
    by_company = TRUE # Output results at company-level
  )

sda_targets_company
```

These results can be saved/written to a CSV file for potential input to other models and software, for example:

```{r}
readr::write_csv(x = sda_targets, file = file.path(tempdir(), "sda_targets.csv"))
readr::write_csv(x = sda_targets_company, file = file.path(tempdir(), "sda_targets_company.csv"))
```

Remember to replace `tempdir()` with the path to the directory that you wish to save your files in.

## Visualize PACTA alignment metrics

A variety of visualizations can be generated from the outputs of `target_market_share()` and `target_sda()`. Below, we highlight a few common plots that can be easily created using the `{pacta.loanbook}` package.

### Market Share: Sector-level technology mix

From the market share output, you can plot the portfolio's exposure to various 
climate sensitive technologies (`projected`), and compare with the corporate 
economy, or against various scenario targets.

```{r technoloy-mix-portfolio}
# Pick the targets you want to plot.
data <- filter(
  market_share_targets_portfolio,
  scenario_source == "demo_2020",
  sector == "power",
  region == "global",
  metric %in% c("projected", "corporate_economy", "target_sds")
)

# Plot the technology mix
qplot_techmix(data)
```

### Market Share: Technology-level volume trajectory

You can also plot the technology-specific volume trend. All starting values are
normalized to 1, to emphasize that we are comparing the rates of build-out and/or
retirement. 

```{r trajetory-portfolio}
data <- filter(
  market_share_targets_portfolio,
  sector == "power",
  technology == "renewablescap",
  region == "global",
  scenario_source == "demo_2020"
)

qplot_trajectory(data)
```

### SDA Target: Sector-level emission intensity

From the SDA output, we can compare the projected average emission intensity 
attributed to the portfolio, with the actual emission intensity scenario, and 
the scenario compliant SDA pathway that the portfolio must follow to achieve 
the scenario ambition by 2050.

```{r sda plot}
data <- filter(sda_targets, sector == "cement", region == "global")
qplot_emission_intensity(data)
```

### Exporting plots to an image file

All of the functions from `{pacta.loanbook}` that produce plots, e.g. `qplot_techmix()` and `plot_trajectory()`, return a `ggplot` object, which can be saved as an image file using the `ggplot2::ggsave()` function, for example:

```{r save_plot_to_file}
emission_intensity_plot <- qplot_emission_intensity(data)

ggplot2::ggsave(
  filename = file.path(tempdir(), "emission_intensity_plot.png"),
  plot = emission_intensity_plot
)
```

Further customization of the image file characteristics can be tweaked using the arguments of `ggplot2::ggsave()`, e.g. `device` (filetype), `width`, `height`, and `dpi` (resolution). See the `ggplot2::ggsave()` documentation for more detail about the options available.

---

**PREVIOUS CHAPTER:** [Preparatory Steps](cookbook_preparatory_steps.html)

**NEXT CHAPTER:** [Interpretation of Results](cookbook_interpretation.html)
