---
title: "Interpretation of Results"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Interpretation of Results}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(pacta.loanbook)
```

## Target Market Share

The target market share approach is used to calculate PACTA alignment metrics for the automotive, coal mining, oil & gas and power sectors. The commonality of these sectors is that there are production pathways by technology or fuel type available for each of them and the asset-based company data is available at the same level of technological granularity as the pathways. As long as these preconditions are fulfilled, the target market share approach could be extended to other sectors. The principle idea of the target market share approach is that every actor in a sector maintains their market share in terms of output units and that each actor reduces their use of high-carbon technologies proportionally, while expanding their use of low carbon technologies so that their market share remains constant, assuming all other actors follow the same approach. In aggregate, this will solve for the scenario changes at the sector level.

For detailed information about the Target Market Share metric and how it is calculated, see the [Metrics appendix](cookbook_metrics.html#market-share-approach).

### `target_market_share()` function

The `target_market_share()` function calculates the Target Market Share metric and outputs a table including the calculated targets at the portfolio level or at the company level, depending on the options selected.

#### Explanation of Output

The primary columns/variables of interest in the output are the `production` and `metric` variables. What the `production` variable represents depends on the values in all of the columns that precede it, and in particular the `metric` column. If the value in the `metric` column on the same row is `"projected"`, then the value in the `production` variable will represent the production level of your portfolio based on the ABCD data for that sector/technology/year/scenario/etc. If the value in the `metric` column on the same row begins with `"target_"`, e.g. `"target_cps"`, then the value in the `production` variable will represent the target level of production for that sector/technology/year/scenario/etc. based on the ABCD start year production value of your portfolio modified to be relative to the scenario data for the given year. If the value in the `metric` column on the same row is `"corporate_economy"`, then the value in the `production` variable will represent the total production levels of the entire sector based on the ABCD for a given region, which can be used as a benchmark to compare to your portfolio's technology mix or production volume trajectory.

For example, the output table could be filtered to view the projected coal power production values for of your portfolio with:

```{r, message = FALSE, warning = FALSE, R.options = list(width = 400)}
dplyr::filter(
  market_share,
  metric == "projected",
  technology == "coalcap"
)
```

The `technology_share` and `percentage_of_initial_production_by_scope` variables also contain values of interest, but they are derivatives of the values contained in the `production` variable. For each `metric`, the `technology_share` variable represents the share of the row's technology within its sector, relative to the production values of other technologies in the same sector, similar to what is shown in the [technology mix plots](cookbook_interpretation.html#technoloy-mix-plot). The `percentage_of_initial_production_by_scope` variable shows the percent change of the production value from the prior year.

If you use the `by_company = TRUE` and the `weight_production = FALSE` options of the `target_market_share()` function, most of what's said above is true except relative to the company listed in that row in the `name_abcd` column.

For detailed information about the table output of the `target_market_share()` function and its columns, see the [data dictionary](data_outputs.html#target_market_share-output).

#### Interpretation & Intuition

[2 or 3 sentences about interpretation]

[2 or 3 sentences about intuition]

### Technoloy Mix Plot

The technology mix metric focuses on technology shifts within the power, fossil fuels and automotive sectors, namely: (i) the changes in the technological processes by which outputs are produced (e.g. shift from coal-fueled to renewable-fueled power capacity), and (ii) changes in the nature of the output itself (e.g. shift from internal combustion engines to electric vehicles). This metric measures the bank’s relative exposure to the economic activities that are impacted by the transition to a low-carbon economy.

#### Explanation of Output

The technology mix plot shows how large a share of each technology the portfolio or company is exposed to in the sector - both at the time of the start of the analysis as well as five years into the future. This projected technology mix of the portfolio is compared to the technology mix in the benchmark region at the same two points in time. And it is compared to the technology mix that the portfolio would have to display five years in the future in order to be aligned with the selected transition scenario. All three types of technology mixes are shown based on assets from the same geographic region, as selected in the analysis.

#### Interpretation & Intuition

For any sector with low-carbon alternatives that can substitute high-carbon products or technologies, the technology mix plot shows the required relative effort to achieve technology shares in line with climate targets. If the low carbon shares of the portfolio/company are larger than those of the benchmark in a given year, then the portfolio/company can be a leader in the sector. If they are smaller than those of the benchmark, then the portfolio/company is a laggard.

In terms of alignment, a portfolio/company is aligned with the scenario if the technology shares of the low-carbon alternatives in the future are at least as large as those of the low-carbon alternatives shown in the technology mix of the climate scenario. 

The overall intuition behind the technology mix plot is that all technologies or fuel types in a sector produce equivalent outputs (e.g. a MWh of electricity has the same use for the end user, regardless of whether it was generated from a coal-fired power plant or a solar panel). Given that the outputs are substitutes and with all else being equal, from an impact angle it can be said that the higher the share of low carbon technologies in the portfolio, the better the result from a climate perspective. From a financial risk angle, the intuition depends a lot on what the user expects the future of the market of a given sector to look like. If the user assumes that transition risk will primarily materialize in the form of carbon pricing, then it is again possible to say that the higher the share of low-carbon technologies in the portfolio, the lower the transition risk. If the user thinks that other, potentially opposing factors could be at play in the sector transition that shape the future of the market, it may be best to pick a scenario that closely resembles that expected future, such that a portfolio technology mix similar to the future scenario technology mix should reduce transition risk.

Generally, it is required to assess the alignment of a portfolio/company not only by the technology mix, but also by the production volume trajectory of the individual technologies of a given sector. This is because the technology mix plot cannot show if the overall output of the portfolio/company grows or declines, even thought he scenario may prescribe an overall production trend for the sector.

```{r, message=FALSE, warning=FALSE, echo=FALSE}
library(pacta.loanbook)

qplot_techmix(
  dplyr::filter(
    market_share,
    scenario_source == "demo_2020",
    sector == "power",
    region == "global",
    metric %in% c("projected", "corporate_economy", "target_sds")
  )
)
```

### Trajectory Plot

The production volume trajectory metric aims to measure the alignment of a portfolio’s projected production volumes, based on the five-year capital expenditure plans of companies, to those given in climate scenarios. It is used for the fossil fuels, power, and automotive sectors. Changes in production volumes result either from transfer of production from one technology to another (e.g. internal combustion engines to electric vehicles) or from sheer expansion or contraction in the production coming from the technology/fuel (e.g. a company brings a new coal-fired power plant online). Projected production volumes at a 5-year horizon are considered at the individual client level at the technology level. The resulting volume trajectories are then compared with the trends set as targets in climate scenarios.

#### Explanation of Output

The production volume trajectory plot shows the production volume of the portfolio or company for one technology (or fuel type) at a time. The plot shows relative changes over a time frame between the start year of the analysis and five years into the future (solid black line). This projected production volume of the portfolio is compared to the production volume in the benchmark region over the same period of time (dashed black line). Finally the background of the plot is shaded in a color scale from red to yellow and green. The lines between the shaded areas represent the relative changes for the technology based on the scenario, using the market share approach. For low-carbon technologies, anything above the most ambitious scenario will be displayed in green, anything below the least ambitious scenario will be displayed in red. For high-carbon technologies, anything below the most ambitious scenario will be displayed in green, anything above the least ambitious scenario will be displayed in red. Generally, the production volume trajectory plot shows multiple scenarios from the same scenario publication, although it also works when comparing the portfolio to a single scenario (the scenario line would split the background in two shaded areas in that case).

#### Interpretation & Intuition

For a technology in a portfolio/company to be perfectly aligned with a climate transition scenario, the production pathway (solid black line) would have to exactly follow the scenario line (the line separating two shaded areas). Low carbon technologies will usually have increasing scenario lines for the more ambitious scenarios. Business-as-usual scenarios for low-carbon technologies can have scenario lines in either direction. For a low-carbon technology, a portfolio/company is aligned with any scenario below the production plans. For a high-carbon technology, a portfolio/company is aligned with any scenario above the production plans.

The intuition is that low-carbon technologies must be scaled up to reach more ambitious climate targets, whereas high-carbon technologies have to be scaled down or, in some cases, even phased out. Therefore, if the production plan of a portfolio/company scales up a low carbon technology faster than the scenario, it contributes strongly to reaching the scenario outcome. conversely, if the portfolio/company does not scale up low-carbon technologies at the scenario pace, it contributes to slowing down the transition below the scenario ambition.

Another aspect about the intuition behind the more ambitious scenarios is that a higher ambition in transitioning to a low-carbon economy (scaling up low-carbon technologies and scaling down high-carbon technologies) correlates with a lower expected global heating outcome.

```{r, message=FALSE, warning=FALSE, echo=FALSE}
library(pacta.loanbook)

qplot_trajectory(
  dplyr::filter(
    market_share,
    sector == "power",
    technology == "renewablescap",
    region == "global",
    scenario_source == "demo_2020"
  )
)
```

## Sectoral Decarbonization (SDA) Target

The sectoral decarbonization approach (SDA) is used to calculate PACTA alignment metrics for the aviation, cement and steel sectors. The commonality of these sectors is that there are no market ready production-pathways at the technology level (or fuel type level) available yet that can be used to describe how to decarbonize the sector activities. They are currently considered "hard-to-abate" sectors. Since there are no market-ready low-carbon alternatives available in these sectors at the moment, that can be scaled up fast, the SDA approach is used to calculate sector-level metrics instead of the technology level metrics available for sectors that use the market share approach. These sector level metrics are production-based emission intensities, such as tonnes of CO~2~ per tonne of cement or tonnes of CO~2~ per tonne of steel. Regardless of how the output unit is produced, this is a comparable measure for the entire sector. The principle idea of the SDA approach is that the required carbon intensity that a sector needs to reach in the future, given assumptions around future production volumes, can be derived by dividing a sector specific carbon budget by the expected production volume. The current GHG emissions divided by the current aggregate sector production volume gives the starting point of the emission intensity. If the actors in a sector decarbonize the production in a way that follows the average emission intensity of the sector, then the scenario assumptions will be solved for in aggregate. At the portfolio/company level, the SDA approach requires every actor to decarbonize their production following their individual trajectory that starts at their current emission intensity and converges on a common emission intensity that is the same for all actors in a sector at the end of the scenario time frame (for example in 2050). This means that a company with an already lower emission intensity will not have to reduce their emission intensity as much as a company that lags the current sector average.

For detailed information about the Sectoral Decarbonization (SDA) metric and how it is calculated, see the [Metrics appendix](cookbook_metrics.html#sectoral-decarbonization-approach).

### `target_sda()` function

The `target_sda()` function calculates the Sectoral Decarbonization Target metric and outputs a table including the calculated targets at the portfolio level or at the company level, depending on the options selected.

#### Explanation of Output

The primary column/variable of interest in the output is the `emission_factor_value` variable. What the `emission_factor_value` variable represents depends on the values in all of the other columns, and in particular the `emission_factor_metric` column. If the value in the `emission_factor_metric` column on the same row is `"projected"`, then the value in the `emission_factor_value` variable will represent the physical emission intensity level of your portfolio based on the ABCD data for that sector/year/region/scenario/etc. If the value in the `emission_factor_metric` column on the same row begins with `"target_"`, e.g. `"target_cps"`, then the value in the `emission_factor_value` variable will represent the target level of physical emission intensity for that sector/year/region/scenario/etc. based on the ABCD start year production value of your portfolio modified to be relative to the scenario data for the given year. If the value in the `emission_factor_metric` column on the same row is `"corporate_economy"`, then the value in the `emission_factor_value` variable will represent [the total physical emission intensity levels of the entire sector adjusted by the start year physical emission intensity level of your portfolio, which can be used aa a benchmark to compare to your portfolio's production levels]. If the value in the `emission_factor_metric` column on the same row starts with `"adjusted_"`, then the value in the `emission_factor_value` variable will represent [?].

If you use the `by_company = TRUE` option of the `target_sda()` function, most of what's said above is true except relative to the company listed in that row in the `name_abcd` column.

For detailed information about the table output of the `target_sda()` function and its columns, see the [data dictionary](data_outputs.html#target_sda-output).

#### Interpretation & Intuition

[2 or 3 sentences about interpretation]

[2 or 3 sentences about intuition]

### Emission Intensity Plot

The emission intensity metric measures the average CO~2~ intensity of the portfolio in the `r cli::format_inline("{unique(co2_intensity_scenario_demo$sector)} sector{?s}")`. This projected emission intensity of a portfolio or company is given as CO~2~/economic unit of output (for example, CO~2~ per ton of steel produced). This five year forward-looking trajectory of the emission intensity is then compared to an emission intensity reference trend over the same period of time based on a climate transition scenario.

The emission intensity of the activities financed by the portfolio is the metric of choice in sectors for which no clear technology pathways have been set out (namely, `r cli::format_inline("{unique(co2_intensity_scenario_demo$sector)}")`). Put differently, for these sectors, no scalable zero-carbon alternative yet exists. As such, it is not possible to use the technology mix metric or the production volume trajectory metric to measure alignment. However, it is still imperative to steer capital in a way that aims to decrease carbon emissions in these sectors – hence the emission intensity metric is used.

#### Explanation of Output

The emission intensity plot shows the projected emission intensity of the portfolio or company (labeled "Projected" in the plot) for a given sector. This is compared to the emission intensity target of the portfolio or company (labeled "Target" in the plot), which starts at the same initial value, but then converges towards a common emission intensity target for all actors in the sector at the end of the scenario time frame. Additionally, the plot show a benchmark trajectory of the emission intensity of the sector (labeled "Corporate Economy" in the plot), which is based on the average of all companies in the given sector and region. The starting point of this benchmark often differs from that of the portfolio or company. Lastly, the plot contains the scenario target for the sector as a whole, based on all companies in the benchmark group (labeled "Adjusted Scenario" in the plot). This is the trend line that the target of the portfolio or company converges towards at the end of the scenario time frame (often 2050 and not always shown in the plot).

#### Interpretation & Intuition

The start value of the portfolio or company relative to the benchmark tells us if the portfolio or company is a leader or a laggard in the sector at the start year of the analysis. If the start value is higher than that of the average, the emission intensity of the portfolio/company is higher than average. This implies that the portfolio/company will have to reduce its emission intensity in the given sector at a steeper rate than the average company, because all emission intensities of the sector need to converge at the end of the scenario time frame and the distance towards that target is higher for a laggard with a high start value than for a leader with a lower than average start value. A portfolio or company is considered aligned with the scenario of the projected emission intensity decreases at a rate at least as steep as the individual target trajectory, as this trend ensures that the portfolio or company will reach the point of convergence at the end of the time frame. Not reaching that level of emission intensity would contribute to jeopardizing the sector target according to the scenario or place a higher burden on other participants to compensate for the lack of ambition. Such a trend, indicated by a projected line higher than the individual scenario target, would therefore be considered misaligned.

The intuition behind the emission intensity plot is that the lower the emission intensity of the portfolio/company, the better the result from a climate perspective. This is because, assuming the overall production of the sector remains constant, the absolute emissions of the sector are lower when the emission intensity is lower which, in turn, leads to less GHG emissions and finally to less global heating.

```{r, message=FALSE, warning=FALSE, echo=FALSE}
library(pacta.loanbook)

qplot_emission_intensity(
  dplyr::filter(
    sda,
    sector == "cement",
    region == "global"
  )
)
```

---

**PREVIOUS CHAPTER:** [Running the Analysis](cookbook_running_the_analysis.html)

**NEXT CHAPTER:** [Advanced Use Cases](cookbook_advanced_use_cases.html)
