---
title: "Classification"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Classification}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, echo = FALSE}
plot_table <- function(table) {
  table_plot <- gt::gt(dplyr::select(table, -"dataset"))
  
  table_plot <- 
    gt::cols_width(
      .data = table_plot,
      column ~ gt::px(150),
      typeof ~ gt::px(90)
    )
  
  table_plot <-
    gt::tab_style(
      data = table_plot,
      style = gt::cell_text(size = "smaller"),
      locations = gt::cells_body(columns = 1:2)
    )
  
  table_plot <-
    gt::tab_options(
      data = table_plot,
      ihtml.active = TRUE,
      ihtml.use_pagination = FALSE,
      ihtml.use_sorting = TRUE,
      ihtml.use_highlight = TRUE
    )
  
  gt::fmt_passthrough(table_plot)
}
```

### GICS classification dataset

This dataset serves as a translation key between the GICS sector-classification system and sectors relevant to the 'PACTA' software.

The `{r2dii.data}` package provides a GICS classification dataset `r2dii.data::gics_classification`.

```{r, echo = FALSE}
table <- dplyr::filter(r2dii.data::data_dictionary, .data[["dataset"]] == "gics_classification")
plot_table(table)
```

### ISIC Rev 5 classification dataset

This dataset serves as a translation key between the ISIC Rev 5 sector-classification system and sectors relevant to the 'PACTA' software.

The `{r2dii.data}` package provides a ISIC Rev 5 classification dataset `r2dii.data::isic_classification`.

```{r, echo = FALSE}
table <- dplyr::filter(r2dii.data::data_dictionary, .data[["dataset"]] == "isic_classification")
plot_table(table)
```

### NACE version 2.1 classification dataset

This dataset serves as a translation key between the NACE version 2.1 sector-classification system and sectors relevant to the 'PACTA' software.

The `{r2dii.data}` package provides a NACE version 2.1 classification dataset `r2dii.data::nace_classification`.

```{r, echo = FALSE}
table <- dplyr::filter(r2dii.data::data_dictionary, .data[["dataset"]] == "nace_classification")
plot_table(table)
```

### PSIC classification dataset

This dataset serves as a translation key between the PSIC sector-classification system and sectors relevant to the 'PACTA' software.

The `{r2dii.data}` package provides a PSIC classification dataset `r2dii.data::psic_classification`.

```{r, echo = FALSE}
table <- dplyr::filter(r2dii.data::data_dictionary, .data[["dataset"]] == "psic_classification")
plot_table(table)
```

### 2DII classification dataset

This dataset serves as a translation key between the 2DII sector-classification system and sectors relevant to the 'PACTA' software.

The `{r2dii.data}` package provides a 2DII classification dataset `r2dii.data::sector_classifications`.

```{r, echo = FALSE}
table <- dplyr::filter(r2dii.data::data_dictionary, .data[["dataset"]] == "sector_classifications")
plot_table(table)
```

### SIC classification dataset

This dataset serves as a translation key between the SIC sector-classification system and sectors relevant to the 'PACTA' software.

The `{r2dii.data}` package provides a SIC classification dataset `r2dii.data::sic_classificatio`.

```{r, echo = FALSE}
table <- dplyr::filter(r2dii.data::data_dictionary, .data[["dataset"]] == "sic_classification")
plot_table(table)
```
