---
title: "Interpretation of Results"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Interpretation of Results}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(pacta.loanbook)
```

This section provides guidance on interpreting key metrics used in PACTA alignment assessments. It explains how different methodologies, including the [Target Market Share](#target-market-share) and [Sectoral Decarbonization](#sectoral-decarbonization-sda-target) approaches, evaluate portfolio alignment with climate transition scenarios. By understanding these outputs users can assess their portfolio’s position relative to sector-wide decarbonization goals and transition risks.

## Target Market Share

The target market share approach is used to calculate PACTA alignment metrics for the automotive, coal mining, oil & gas and power sectors. These sectors share two key characteristics:

- production pathway scenarios are available by technology or fuel type
- asset-based company data at the same level of technological granularity is also available

The target market share approach can be extended to any sector that meets these conditions. The core idea is that each actor maintains a constant market share in output units while proportionally reducing high-carbon technologies and increasing low-carbon alternatives, assuming all actors follow the same strategy. In aggregate, this ensures alignment with the sector’s transition pathway.

For more details on the Target Market Share metric and its calculation, see the [Metrics appendix](cookbook_metrics.html#market-share-approach).

### `target_market_share()` function

The `target_market_share()` function calculates the Target Market Share metric and outputs a table including the calculated targets at the portfolio level or at the company level, depending on the options selected.

#### Explanation of Output

The primary variables of interest in the output are `production` and `metric`. The `production` variable's meaning depends on the `metric` column and other preceding columns. If `metric` is `"projected"`, then `production` represents the portfolio’s projected production output based on ABCD data for the specified sector, technology, year, and scenario. If `metric` starts with `"target_"` (e.g., `"target_cps"`), production represents the target production level for that `sector` and `scenario`, derived from the portfolio’s initial ABCD production and following the relative required changes of the scenario according to the market share approach. If `metric` is `"corporate_economy"`, then `production` reflects the total sector production in a given region, calculated using the ABCD. This serves as a benchmark for comparison.

For example, the output table could be filtered to view the projected coal power production values for your portfolio:

```{r, message = FALSE, warning = FALSE, R.options = list(width = 400)}
dplyr::filter(
  market_share,
  metric == "projected",
  technology == "coalcap"
)
```

Additional variables include `technology_share`, which represents the share of a given technology within the sector, and `percentage_of_initial_production_by_scope`, which shows the percent change in `production` from the previous year. Both are derived from the `production` variable. The `technology_share` values can be visualized in the [technology mix plots](cookbook_interpretation.html#technoloy-mix-plot). 

If `by_company = TRUE` and `weight_production = FALSE` are used in `target_market_share()`, the output is interpreted relative to the company listed in the `name_abcd` column.

For a detailed breakdown of `target_market_share()`'s output table and its columns, see the [data dictionary](data_outputs.html#target_market_share-output).

### Technoloy Mix Plot

The technology mix metric tracks shifts in production methods and outputs within the power, fossil fuels and automotive sectors. It captures:

- (i) changes in production technology (e.g., transitioning from coal-fueled to renewable power production)
- (ii) changes in output type (e.g. shift from internal combustion engines to electric vehicles). 

This metric measures the bank’s exposure to the economic activities that are impacted by the transition to a low-carbon economy.

#### Explanation of Output

The technology mix plot illustrates the share of each technology in a portfolio or company at the analysis start and five years into the future. It compares the portfolio’s projected technology mix to both the benchmark region’s mix at the same time points and the mix required for alignment with the selected transition scenario. All comparisons are based on assets from the same geographic region as defined in the analysis.

#### Interpretation & Intuition

The technology mix plot illustrates the effort required to align a portfolio’s technology shares with climate targets. If a portfolio or company has a higher share of low-carbon technologies than the benchmark in a given year, it is considered a leader; if lower, it is a laggard. Alignment with the scenario occurs when the portfolio’s future low-carbon technology shares meet or exceed those in the scenario’s technology mix.

The underlying intuition is that all technologies in a sector produce equivalent outputs (e.g., a MWh of electricity, regardless of source). From a climate impact perspective, a higher share of low-carbon technologies is preferable. From a financial risk perspective, the implications depend on market expectations. If, for example, transition risk is expected to materialize through carbon pricing, then higher low-carbon shares reduce risk. However, if other factors influence sector transitions, selecting a scenario that mirrors expected market trends can help mitigate that risk.

To fully assess alignment, technology mix should be evaluated alongside production volume trajectory, as the technology mix plot alone does not indicate whether overall output is increasing or decreasing, even if a scenario prescribes a specific production trend.


```{r, message=FALSE, warning=FALSE, echo=FALSE}
library(pacta.loanbook)

qplot_techmix(
  dplyr::filter(
    market_share,
    scenario_source == "demo_2020",
    sector == "power",
    region == "global",
    metric %in% c("projected", "corporate_economy", "target_sds")
  )
)
```

### Trajectory Plot

The production volume trajectory metric evaluates a portfolio’s alignment with climate scenarios by comparing projected production volumes---based on companies' five-year capital expenditure plans---to scenario targets. It applies to the fossil fuels, power, and automotive sectors, where production changes occur either through shifts between technologies (e.g., internal combustion engines to electric vehicles) or overall expansion/contraction (e.g., adding new coal-fired power plants). The trajectory reflects these changes at the technology level for individual clients and is compared to climate scenario trends.

#### Explanation of Output

The trajectory plot displays a portfolio’s production volume for a specific technology or fuel type, tracking changes from the start year to five years into the future (**solid black line**). This projection is compared to the benchmark region’s production trajectory (**dashed black line**). The plot’s background is color-coded: green indicates alignment with ambitious climate scenarios, red signifies misalignment, and shades of yellow for in-between. For low-carbon technologies, values above the most ambitious scenario appear green, and those below the least ambitious scenario appear red; the opposite applies to high-carbon technologies. Typically, the plot includes multiple scenarios but can also compare the portfolio against a single scenario.

#### Interpretation & Intuition

A portfolio is aligned with a climate scenario if its production trajectory (**solid black line**) follows the scenario line. Low-carbon technologies generally require increasing production under ambitious scenarios, whereas high-carbon technologies must decline or phase-out. If a portfolio scales up low-carbon production faster than the scenario, it supports the transition; if it lags, it slows progress.

More ambitious scenarios assume stronger shifts toward low-carbon solutions, leading to lower global heating outcomes. Thus, the degree of ambition in a portfolio’s production trajectory directly correlates to its alignment with climate targets.

```{r, message=FALSE, warning=FALSE, echo=FALSE}
library(pacta.loanbook)

qplot_trajectory(
  dplyr::filter(
    market_share,
    sector == "power",
    technology == "renewablescap",
    region == "global",
    scenario_source == "demo_2020"
  )
)
```

## Sectoral Decarbonization (SDA) Target

The sectoral decarbonization approach (SDA) is used to calculate PACTA alignment metrics for the aviation, cement and steel sectors. The commonality of these sectors is that there are no market ready production-pathways at the technology level (or fuel type level) available yet that can be used to describe how to decarbonize the sector activities. They are currently considered "hard-to-abate" sectors. Since there are no market-ready low-carbon alternatives available in these sectors at the moment, that can be scaled up fast, the SDA approach is used to calculate sector-level metrics instead of the technology level metrics available for sectors that use the market share approach. These sector level metrics are production-based emission intensities, such as tonnes of CO~2~ per tonne of cement or tonnes of CO~2~ per tonne of steel. Regardless of how the output unit is produced, this is a comparable measure for the entire sector. The principle idea of the SDA approach is that the required carbon intensity that a sector needs to reach in the future, given assumptions around future production volumes, can be derived by dividing a sector specific carbon budget by the expected production volume. The current GHG emissions divided by the current aggregate sector production volume gives the starting point of the emission intensity. If the actors in a sector decarbonize the production in a way that follows the average emission intensity of the sector, then the scenario assumptions will be solved for in aggregate. At the portfolio/company level, the SDA approach requires every actor to decarbonize their production following their individual trajectory that starts at their current emission intensity and converges on a common emission intensity that is the same for all actors in a sector at the end of the scenario time frame (for example in 2050). This means that a company with an already lower emission intensity will not have to reduce their emission intensity as much as a company that lags the current sector average.

For detailed information about the Sectoral Decarbonization (SDA) metric and how it is calculated, see the [Metrics appendix](cookbook_metrics.html#sectoral-decarbonization-approach).

### `target_sda()` function

The `target_sda()` function calculates the Sectoral Decarbonization Target metric and outputs a table including the calculated targets at the portfolio level or at the company level, depending on the options selected.

#### Explanation of Output

The primary column/variable of interest in the output is the `emission_factor_value` variable. What the `emission_factor_value` variable represents depends on the values in all of the other columns, and in particular the `emission_factor_metric` column. If the value in the `emission_factor_metric` column on the same row is `"projected"`, then the value in the `emission_factor_value` variable will represent the physical emission intensity level of your portfolio based on the ABCD data for that sector/year/region/scenario/etc. If the value in the `emission_factor_metric` column on the same row begins with `"target_"`, e.g. `"target_cps"`, then the value in the `emission_factor_value` variable will represent the target level of physical emission intensity for that sector/year/region/scenario/etc. This target level is derived based on the ABCD emission intensity value of your portfolio in the start year and converging with the emission intensity of the scenario in the final year. If the value in the `emission_factor_metric` column on the same row is `"corporate_economy"`, then the value in the `emission_factor_value` variable will represent the weighted average physical emission intensity of the entire sector, which can be used as a benchmark to compare to your portfolio's emission intensity levels. If the value in the `emission_factor_metric` column on the same row starts with `"adjusted_"`, then the value in the `emission_factor_value` variable will represent the scenario trajectory of the emission intensity, adjusted for differences between the sector totals in the ABCD and the scenario data.

If you use the `by_company = TRUE` option of the `target_sda()` function, most of what's said above is true except relative to the company listed in that row in the `name_abcd` column.

For detailed information about the table output of the `target_sda()` function and its columns, see the [data dictionary](data_outputs.html#target_sda-output).

### Emission Intensity Plot

The emission intensity metric measures the average CO~2~ intensity of the portfolio in the `r cli::format_inline("{unique(co2_intensity_scenario_demo$sector)} sector{?s}")`. This projected emission intensity of a portfolio or company is given as CO~2~/economic unit of output (for example, CO~2~ per ton of steel produced). This five year forward-looking trajectory of the emission intensity is then compared to an emission intensity reference trend over the same period of time based on a climate transition scenario.

The emission intensity of the activities financed by the portfolio is the metric of choice in sectors for which no clear technology pathways have been set out (namely, `r cli::format_inline("{unique(co2_intensity_scenario_demo$sector)}")`). Put differently, for these sectors, no scalable zero-carbon alternative yet exists. As such, it is not possible to use the technology mix metric or the production volume trajectory metric to measure alignment. However, it is still imperative to steer capital in a way that aims to decrease carbon emissions in these sectors – hence the emission intensity metric is used.

#### Explanation of Output

The emission intensity plot shows the projected emission intensity of the portfolio or company (labeled "Projected" in the plot) for a given sector. This is compared to the emission intensity target of the portfolio or company (labeled "Target" in the plot), which starts at the same initial value, but then converges towards a common emission intensity target for all actors in the sector at the end of the scenario time frame. Additionally, the plot show a benchmark trajectory of the emission intensity of the sector (labeled "Corporate Economy" in the plot), which is based on the average of all companies in the given sector and region. The starting point of this benchmark often differs from that of the portfolio or company. Lastly, the plot contains the scenario target for the sector as a whole, based on all companies in the benchmark group (labeled "Adjusted Scenario" in the plot). This is the trend line that the target of the portfolio or company converges towards at the end of the scenario time frame (often 2050 and not always shown in the plot).

#### Interpretation & Intuition

The start value of the portfolio or company relative to the benchmark tells us if the portfolio or company is a leader or a laggard in the sector at the start year of the analysis. If the start value is higher than that of the average, the emission intensity of the portfolio/company is higher than average. This implies that the portfolio/company will have to reduce its emission intensity in the given sector at a steeper rate than the average company, because all emission intensities of the sector need to converge at the end of the scenario time frame and the distance towards that target is higher for a laggard with a high start value than for a leader with a lower than average start value. A portfolio or company is considered aligned with the scenario of the projected emission intensity decreases at a rate at least as steep as the individual target trajectory, as this trend ensures that the portfolio or company will reach the point of convergence at the end of the time frame. Not reaching that level of emission intensity would contribute to jeopardizing the sector target according to the scenario or place a higher burden on other participants to compensate for the lack of ambition. Such a trend, indicated by a projected line higher than the individual scenario target, would therefore be considered misaligned.

The intuition behind the emission intensity plot is that the lower the emission intensity of the portfolio/company, the better the result from a climate perspective. This is because, assuming the overall production of the sector remains constant, the absolute emissions of the sector are lower when the emission intensity is lower which, in turn, leads to less GHG emissions and finally to less global heating.

```{r, message=FALSE, warning=FALSE, echo=FALSE}
library(pacta.loanbook)

qplot_emission_intensity(
  dplyr::filter(
    sda,
    sector == "cement",
    region == "global"
  )
)
```

---

**PREVIOUS CHAPTER:** [Running the Analysis](cookbook_running_the_analysis.html)

**NEXT CHAPTER:** [Advanced Use Cases](cookbook_advanced_use_cases.html)
